
---
title: "China landing page analysis"
author: "Alexey Antonitsin"
date: "Monday, November 03, 2014"
output: ioslides_presentation
---

## Project goal



- understand traffic source for Chinese users who landing on eBay Today and Haitao pages  
- visualize chart  
- understand main engagement activities



## Steps

- Get sessions where landing page is either EBT or Haitao and their traffic source
- Plot 1: Distribution by BBOWAC Distribution of visits by traffic source and by page type
- Plot 2: Distribution of visits by traffic source and by page type

## Getting data

Uploading libraries and pulling data
```{r, warning=FALSE}


library(ggplot2)
library(ebaytd)
library(plyr)
c <- teradataConnect()
s <-  "
Select user_gr, succ_evnt_type, count(distinct guid) vstrs
  from  p_alexey_t.ch_lp_groups_bbowa
  group by 1,2
"
df <- dbGetQuery(c,s)


```

## Correcting datatypes

Datatypes seems off, so we need to correct them
```{r, warning=FALSE}

str(df)
names(df)<-make.names(names(df), unique = FALSE, allow_ = TRUE)
names(df) <- tolower(names(df))
df$user_gr<-as.factor(df$user_gr)
df$succ_evnt_type<-as.factor(df$succ_evnt_type)


```

## Pivoting the data

Data is not quite the right format, so we need to reshape it
```{r, warning=FALSE, comment=FALSE,message=FALSE,  error=FALSE, results=FALSE}


table<-ddply(df,c("succ_evnt_type", "user_gr"),
             summarize, sum_visitors=sum(vstrs, na.rm=TRUE))
library(reshape)
pivot <- cast(table, succ_evnt_type~user_gr, sum)


```

## Plotting the data

Using qplot to plot the data
```{r,  results=FALSE, message=FALSE, warning=FALSE}

qplot(succ_evnt_type, data=table, geom="bar", binwidth = 0.1,
      weight=sum_visitors, ylim = c(0,1000), facets = . ~ user_gr)

```


## Same with traffic source

Repeating the analysis for traffic source
```{r, warning=FALSE, results='hide', message=FALSE,}

d <- teradataConnect()
f <- "
select pagetype, session_traffic_source_id, count(unique guid) from p_alexey_t.ch_lp_large
where pagetype in ('coll', 'Haitao')
group by 1,2
"
df_2 <- dbGetQuery(d,f)
str(df_2)
df_2$pagetype<-as.factor(df_2$pagetype)
df_2$session_traffic_source_id<-as.factor(df_2$session_traffic_source_id)



```

## Plot 2

```{r, echo=FALSE}
#plotting data

qplot(session_traffic_source_id, data=df_2, geom="bar", binwidth = 0.1,
weight=guid,  facets = . ~ pagetype)
```


